\papertitle

### 2025-01-22 src/tex/ms.tex
[showyourwork] overleaf sync

To demonstrate the effectiveness of our \emph{psuedo}-centre of mass recentering extension, \cref{fig:method_comparison} compares it to the Bai and Breen method.
To achieve this, we compute the difference between the estimated centre of mass and the true value, as a ratio of the span of the particle group. 
This error is compared with the asymmetry of the particle mass density in the periodic cell\cite{xioajun_on_1991}.
In \cref{fig:method_comparison} as the asymmetry increases, so does the error in the Bai and Breen approach. 
However, the \emph{psuedo}-centre of mass resampling is not affected in this way. 
Therefore, for the majority of chemical simulations, this \emph{pseudo}-center of mass recentering extension should be used to ensure accuracy in centre of mass calculation. 
%
\begin{figure}
    \centering
    \includegraphics[width=8cm]{Fig3.pdf}
    \caption{Error in Bai and Breen method (blue shading representing 1, 2, and 3$\sigma$ spreads) compared with the \emph{psuedo} centre of mass recentering approach (orange line). 
    $2^24$ random configurations of one-dimensional periodic boundary spanning molecules were generated, with between 3 and 512 atoms and total length of less than half the box. 
    For each configuration, the two approaches were used and the asymmetry of the molecule\cite{xioajun_on_1991} was compared to the error in the estimate normalised by the span (length) of the molecule. 
    The results have been binned along the the $x$-axis using 100 bins, spaced evenly on a log scale.}
    \label{fig:method_comparison}
    \script{Fig3.py}
\end{figure}
%

>>>>

To demonstrate the effectiveness of our \emph{psuedo}-centre of mass recentering extension, \cref{fig:method_comparison} compares it to the Bai and Breen method.
To achieve this, we compute the difference between the estimated centre of mass and the true value, as a ratio of the span of the particle group. 
This error is compared with the asymmetry of the particle mass density in the periodic cell\cite{xioajun_on_1991}.
In \cref{fig:method_comparison} as the asymmetry increases, so does the error in the Bai and Breen approach. 
However, the \emph{psuedo}-centre of mass resampling is not affected in this way. 
Therefore, for the majority of chemical simulations, this \emph{pseudo}-center of mass recentering extension should be used to ensure accuracy in centre of mass calculation. 
%
\begin{figure}
    \centering
    \includegraphics[width=8cm]{Fig3.pdf}
    \caption{Error in Bai and Breen method (blue shading representing 1, 2, and 3$\sigma$ spreads) compared with the \emph{psuedo} centre of mass recentering approach (orange line). 
    $2^{24}$ random configurations of one-dimensional periodic boundary spanning molecules were generated, with between 3 and 512 atoms and total length of less than half the box. 
    For each configuration, the two approaches were used and the asymmetry of the molecule\cite{xioajun_on_1991} was compared to the error in the estimate normalised by the span (length) of the molecule. 
    The results have been binned along the the $x$-axis using 100 bins, spaced evenly on a log scale.}
    \label{fig:method_comparison}
    \script{Fig3.py}
\end{figure}
%
